Visualize atlantisom

### 2021-01-29 Visualize_atlantisom.Rmd
changed year range in MSE paper figure

plotsurv <- ggplot() +
  geom_line(data=omTrueB, aes(x=time/stepperyr,y=totB, color="True total B"), 
            alpha = 10/10) +
  geom_point(data=survObsBiomB, aes(x=time/stepperyr,y=atoutput, color="Survey sample B"), 
            alpha = 10/10) +
  xlab("") + 
  ylab("") +
  scale_color_manual(values=c(mycol[2], mycol[1]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("blank", "solid"),
                         shape = c(16, NA)))) + 
  xlim(0,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="Atlantis-sardine")

plotSSfit <- ggplot() +
  geom_line(data=index_data_fits, aes(x=Yr,y=Exp,color="SS3 est. survey B"), 
            alpha = 10/10, size=2) +
  geom_pointrange(data=index_data_fits, 
                  aes(x=Yr,y=Obs,
                      ymin=exp(log(Obs)+qt(0.025,df=output_from_SS$survey_error[2])*SE),
                      ymax=exp(log(Obs)+qt(0.975,df=output_from_SS$survey_error[2])*SE),
                      fatten = .5,
                      color="Survey B + error"),
                  alpha = 10/10) + 
  scale_x_continuous(limits = c(0,120), breaks = seq(0,125,25)) +
  xlab("") + 
  ylab("Biomass, t") +
  scale_color_manual(values=c(mycol[3], mycol[2]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("solid", "blank"),
                         shape = c(NA, 16)))) + 
  xlim(0,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="SS3-survey fit")

plotSSskill <- ggplot() +
  geom_line(data=omTrueB, aes(x=time/stepperyr,y=totB, color="True total B"), 
            alpha = 10/10) +
  geom_point(data=output_from_SS$timeseries, aes(x=Yr,y=Bio_all, color="SS3 est. total B"),
             alpha = 10/10) + 
  xlab("Year") + 
  ylab("") +
  scale_color_manual(values=c(mycol[3], mycol[1]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("blank", "solid"),
                         shape = c(16, NA)))) + 
  xlim(0,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="SS3-biomass skill")

>>>>

plotsurv <- ggplot() +
  geom_line(data=omTrueB, aes(x=time/stepperyr,y=totB, color="True total B"), 
            alpha = 10/10) +
  geom_point(data=survObsBiomB, aes(x=time/stepperyr,y=atoutput, color="Survey sample B"), 
            alpha = 10/10) +
  xlab("") + 
  ylab("") +
  scale_color_manual(values=c(mycol[2], mycol[1]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("blank", "solid"),
                         shape = c(16, NA)))) + 
  xlim(20,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="Atlantis-sardine")

plotSSfit <- ggplot() +
  geom_line(data=index_data_fits, aes(x=Yr,y=Exp,color="SS3 est. survey B"), 
            alpha = 10/10, size=2) +
  geom_pointrange(data=index_data_fits, 
                  aes(x=Yr,y=Obs,
                      ymin=exp(log(Obs)+qt(0.025,df=output_from_SS$survey_error[2])*SE),
                      ymax=exp(log(Obs)+qt(0.975,df=output_from_SS$survey_error[2])*SE),
                      fatten = .5,
                      color="Survey B + error"),
                  alpha = 10/10) + 
  scale_x_continuous(limits = c(0,120), breaks = seq(0,125,25)) +
  xlab("") + 
  ylab("Biomass, t") +
  scale_color_manual(values=c(mycol[3], mycol[2]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("solid", "blank"),
                         shape = c(NA, 16)))) + 
  xlim(20,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="SS3-survey fit")

plotSSskill <- ggplot() +
  geom_line(data=omTrueB, aes(x=time/stepperyr,y=totB, color="True total B"), 
            alpha = 10/10) +
  geom_point(data=output_from_SS$timeseries, aes(x=Yr,y=Bio_all, color="SS3 est. total B"),
             alpha = 10/10) + 
  xlab("Year") + 
  ylab("") +
  scale_color_manual(values=c(mycol[3], mycol[1]),
                     guide = guide_legend(override.aes = list(
                         linetype = c("blank", "solid"),
                         shape = c(16, NA)))) + 
  xlim(20,80) +
  theme_tufte() +
  theme(legend.position = "right") +
  labs(colour="SS3-biomass skill")
